|

### 2016-05-27 Benchmark/MSGF-Benchmark/msgf-benchmark2.Rmd
skip filtering option

#3. Differences. Spec eValue = `r evalue` 
### a. From PNNL
```{r, echo=F}
c_pnnl = pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
# No of remaining scans 
nrow(c_pnnl)
head(c_pnnl,2)
tail(c_pnnl,2)

@@

### a. From Docker
```{r, echo=F}
c_docker = docker[docker$Spec_Evalue<evalue,]
# No of remaining scans 
nrow(c_docker)
head(c_docker,2)
tail(c_docker,2)
```

>>>>

#3. Differences. Spec eValue = `r evalue` 
### a. From PNNL
```{r, echo=F}
c_pnnl = pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
print(paste("Remaining peptides:",nrow(c_pnnl)))
print("====== head ======")
head(c_pnnl,2)
print("====== tail ======")
tail(c_pnnl,2)

@@

### a. From Docker
```{r, echo=F}
c_docker = docker[docker$Spec_Evalue<evalue,]
print(paste("Remaining peptides:",nrow(c_docker)))
print("====== head ======")
head(c_docker,2)
print("====== tail ======")
tail(c_docker,2)
```
